---
title: "GSS challange"
author: "Maryana Maayah"
date: "october 8, 2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
GSS <-read.csv(file="GSScsv.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is belief in the bigbang theory (BIGBANG) independent of belief in an afterlife (POSTLIFE)?
we are looking at data from the GSS data set , specifically the BIGBANG and postlife variables, to determine weather or not there is a correlation between belife in the big bang theoru and belief in the afterlife.

$H_0$ There is no correlation between belief in the Big Bang theory and belief in the afterlife.   

$H_A$ There is a correlation between belief in the Big Bang theory and belief in the afterlife.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
  
because the variables we are looking at are both categorical, we are using a bar plot and table for our graphical and numerical results.    
  
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->
  
## Descriptive Results

### Graphical Descriptive Results
```{r}
barchartGC(~BIGBANG + POSTLIFE,data=GSS)
barchartGC(~BIGBANG + POSTLIFE,data=GSS, type="percent")

```
  
According to the bar chart, it appears that there may not be a correlation between belief in the Big Bang Theory and belief in the afterlife. Regardless of belief in the Big Bang Theory, belief in the afterlife was high in both categories (true/false).   
  
<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

### Numerical Descriptive Results
```{r}
table1 <- xtabs(~BIGBANG + POSTLIFE, data=GSS)
rowPerc(table1)
colPerc(table1)
```

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
According to the table, 91.67 percent of people who do not believe in the Big Bang theory do believe in an afterlife. 81.71 percent of people who do believe in the Big Bang theory also believe in an afterlife. It does not appear that there is a correlation between the two beliefs.  
  
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
The p-value is 0.08 which is greater than 0.05. Therefore, we fail to reject the null hypothesis. From the data and the p-value found in the inferential results, we do not see a correlation between belief in the Big Bang theory and belief in the afterlife.  
  
